The Proofs

### 2024-02-13 proofs/tex/singularity-statements.tex
wip

\begin{restatable}[Soundness of Entry Singularity]{lemma}{lemEntrySingularitySoundness}
    \label{lemma:entry-singularity-soundness}
    \hfill
    \begin{itemize}
        \item [$+$] Suppose $[[scE singular with iP]]$ for $[[iP]]$ well-formed in $[[Γ]]$.
            Then $[[ Γ ⊢ iP : scE ]]$
            and for any $[[ Γ ⊢ iP']]$ such that $[[Γ ⊢ iP' : scE]]$, $[[Γ ⊢ iP' ≈ iP]]$;
        \item [$-$] Suppose $[[scE singular with iN]]$ for $[[iN]]$ well-formed in $[[Γ]]$.
            Then $[[ Γ ⊢ iN : scE ]]$
            and for any $[[ Γ ⊢ iN']]$ such that $[[Γ ⊢ iN' : scE]]$, $[[Γ ⊢ iN' ≈ iN]]$.
    \end{itemize}
\end{restatable}

@@

\begin{restatable}[Soundness of Singularity]{lemma}{lemSingularitySoundness}
    \label{lemma:singularity-soundness}
    Suppose $[[Θ ⊢ SC : Ξ]]$, and $[[SC singular with uσ]]$. 
    Then $[[ Θ ⊢ uσ : Ξ ]]$,
     $[[ Θ ⊢ uσ : SC ]]$ and for any 
    $[[uσ']]$ such that $[[Θ ⊢ uσ : SC]]$,
    $[[Θ ⊢ uσ' ≈ uσ : Ξ]]$.
\end{restatable}

>>>>

\begin{restatable}[Soundness of Minimal Instantiation]{lemma}{lemMinInstSoundness}
    \label{lemma:min-inst-soundness}
    Suppose that $[[Γ ⊢ Θ]]$, $[[Θ ⊢ SC]]$, and $[[Γ; dom(Θ) ⊢ uP]]$.
    If $[[Γ ⊢ uP SC minby uσ ]]$ then
    \begin{itemize}
        \item $[[Θ ⊢ uσ : uv uP]]$,
        \item $[[Θ ⊢ uσ : SC]]$,
        \item $[[uσ]]$ is normalized, and
        \item for any other $[[Θ ⊢ uσ' : uv uP ]]$
            respecting $[[SC]]$ (\ie $[[Θ ⊢ uσ' : SC]]$), we have
            $[[Γ ⊢ [uσ']uP ≥ [uσ]uP ]]$. 
    \end{itemize}
\end{restatable}

\begin{restatable}[Completeness of Minimal Instantiation]{lemma}{lemMinInstCompleteness}
    \label{lemma:min-inst-completeness}
    Suppose that $[[Γ ⊢ Θ]]$, $[[Θ ⊢ SC]]$, $[[Γ; dom(Θ) ⊢ uP]]$, and there exists 
    $[[Θ ⊢ uσ : uv uP ]]$ respecting $[[SC]]$ ($[[Θ ⊢ uσ : SC]]$) 
    such that for any other $[[Θ ⊢ uσ' : uv uP ]]$
    respecting $[[SC]]$ ($[[Θ ⊢ uσ' : SC]]$), we have
    $[[Γ ⊢ [uσ']uP ≥ [uσ]uP ]]$. 
    Then $[[Γ ⊢ uP SC minby nf(uσ) ]]$.
\end{restatable}

\begin{restatable}[Minimal Instantiation is Deterministic]{observation}{obsMinInstDeterministic}
    Suppose that $[[Γ ⊢ Θ]]$, $[[Θ ⊢ SC]]$, $[[Γ; dom(Θ) ⊢ uP]]$.
    Then $[[Γ ⊢ uP SC minby uσ]]$ and $[[Γ ⊢ uP SC minby uσ']]$ implies $[[uσ = uσ']]$.
\end{restatable}

\begin{restatable}[Soundness of Entry Singularity]{lemma}{lemEntrySingularitySoundness}
    \label{lemma:entry-singularity-soundness}
    \hfill
    \begin{itemize}
        \item [$+$] Suppose $[[scE singular with iP]]$ for $[[iP]]$ well-formed in $[[Γ]]$.
            Then $[[ Γ ⊢ iP : scE ]]$, $[[iP]]$ is normalized, 
            and for any $[[ Γ ⊢ iP']]$ such that $[[Γ ⊢ iP' : scE]]$, $[[Γ ⊢ iP' ≈ iP]]$;
        \item [$-$] Suppose $[[scE singular with iN]]$ for $[[iN]]$ well-formed in $[[Γ]]$.
            Then $[[ Γ ⊢ iN : scE ]]$, $[[iN]]$ is normalized,
            and for any $[[ Γ ⊢ iN']]$ such that $[[Γ ⊢ iN' : scE]]$, $[[Γ ⊢ iN' ≈ iN]]$.
    \end{itemize}
\end{restatable}

@@

\begin{restatable}[Soundness of Singularity]{lemma}{lemSingularitySoundness}
    \label{lemma:singularity-soundness}
    Suppose $[[Θ ⊢ SC : Ξ]]$, and $[[SC singular with uσ]]$. 
    Then $[[ Θ ⊢ uσ : Ξ ]]$, 
     $[[ Θ ⊢ uσ : SC ]]$, $[[uσ]]$ is normalized, and for any 
    $[[uσ']]$ such that $[[Θ ⊢ uσ : SC]]$,
    $[[Θ ⊢ uσ' ≈ uσ : Ξ]]$.
\end{restatable}
